Presentasjon OPX Fiffig tittel

### 2022-08-02 Presentasjon/presentasjon.Rmd
Flere bilder

# Introduction

## <br> OPX and their goal
- A startup developing solutions for socially responsible investment strategies
- The goal is to increase cash flow to charitable purposes 
- Donors' trust in NGOs' financial performance and their ability to deliver results is crucial for their choice of beneficients <br>

@@

@@

>>>>

## {data-background="Images/start1.png" data-background-size=cover}

## <br> OPX and their goal
- Develop solutions for socially responsible investment strategies
- Increase cash flow to charitable purposes <br>

@@

## {data-background="Images/fcuk.png" data-background-size=cover}

@@

## <iframe width="1280" height="720" src="Images/henrik.mp4" align="middle" frameborder="0" allowfullscreen></iframe>
